SPARQL on the Open, Decentralised Web

### 2016-11-14 dissertation/papersincontext.tex
Mention frank's laws
The problem-paper mapping table #31

@@

\begin{quote}
Kjetil Kjernsmo.
\newblock A Survey of HTTP Caching Implementations on the Open Semantic Web.
\Newblock In Fabien Gandon, Marta Sabou, Harald Sack, Claudia d’Amato,
  Philippe Cudré-Mauroux, and Antoine Zimmermann, editors, {\em The Semantic
  Web. Latest Advances and New Domains}, volume 9088 of {\em Lecture Notes in
  Computer Science}, pages 286--301. Springer International Publishing, 2015.
\end{quote}

@@

@@

>>>>

The discussion of the problems include references to the problems
discussed in Section~\ref{sec:problems}, and the relationship can also
be found in the overview Table~\ref{tab:problempaper}.

@@

\begin{quote}
Kjetil Kjernsmo.
\newblock A Survey of HTTP Caching Implementations on the Open Semantic Web.
\newblock In Fabien Gandon, Marta Sabou, Harald Sack, Claudia d’Amato,
  Philippe Cudré-Mauroux, and Antoine Zimmermann, editors, {\em The Semantic
  Web. Latest Advances and New Domains}, volume 9088 of {\em Lecture Notes in
  Computer Science}, pages 286--301. Springer International Publishing, 2015.
\end{quote}

@@

Also, the investigation would be deeper if it tried to address
Problem~\ref{prob:lawsfuture}. A single analysis would not be
sufficient to do that, laws would require multiple studies over time.

@@

\begin{table}{h}
  \caption{The relationship between the identified problems and the
    papers that make contributions towards solving them.}\label{tab:problempaper}

  \begin{tabular}{|l|l|}
    \hline
    Paper & Problems \\
    \hline
    Hypermedia RDF (Section~\ref{sec:conlapis}) &
    Developer-understandable interface (Problem~\ref{prob:lapis}) \\
    Design of Experiments (Section~\ref{sec:condoe}) & Statistical
    methodologies (Problem~\ref{prob:badstats}) \\
    Low-level complexity (Section~\ref{sec:conpush}) &
    Practical evaluation
    problems~\ref{prob:breakdown},~\ref{prob:complexapi}~and~\ref{prob:dontjustpass}
    \\
    Caching survey (Section~\ref{sec:consanity}) &
    Unknown cache support (Problem~\ref{prob:sanity}) \\
    Philosophy of Science (Section~\ref{sec:conphil}) & Inadequate
    philosophical foundation (Problem~\ref{prob:badphil}) \\
    \hline
  \end{tabular}
\end{table}
